% !TEX program = xelatex
\documentclass[12pt]{resume}
\usepackage{fontawesome6}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hanging}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Chentao Fan}

\basicInfo{
  \email{cxf373@case.edu} \textperiodcentered\
  \phone{(216)303-2715} \textperiodcentered\
  \github[Aphcity]{https://github.com/Aphcity} \textperiodcentered\
  \linkedin[Chentao Fan]{https://www.linkedin.com/in/chentao-fan-9192a5324/}
}

\section{\texorpdfstring{\textbf{\faicon{graduation-cap}}\ Education}{Education}}
\datedsubsection{\textbf{Case Western Reserve University}, Cleveland, U.S.A.}{2024 -- Present}
\textit{Master of Science} in Computer Science (CS), expected May 2027
\datedsubsection{\textbf{China University of Mining \& Technology(Beijing)}, Beijing, China}{2018 -- 2022}
\textit{Bachelor of Engineering} in Electronics Engineering and Automation (EE)

\section{\texorpdfstring{\textbf{\faicon{city}}\ Internships}{Internships}}
\datedsubsection{\textbf{Shanxi Sensor \& Control Electronics Technology Co., Ltd}, Shanxi, China}{Jun. 2024 -- Aug. 2024}
\role{C, keil, ARM, Linux}{Software Engineer}
Brief introduction:
Using STC8H8K64U MCU and OneNet Open IoT to control the valve.
\begin{itemize}
  \item Implemented angle control and NFC-controlled function of valves.
  \item Optimized the command protocol on both client and platform sides.
  \item Developed the PWM-controlled buzzer module with adjustable frequency and duty cycle.
  \item Implemented an ADC module-controlled motor with temperature and angle sensors.
  \item Composed complete reference documents for this project.
\end{itemize}

\datedsubsection{\textbf{Shanxi Tongwen Vocational and Technical College}, Shanxi, China}{Nov. 2022 -- Oct. 2023}
\role{C, C\#}{Tutor Assistant}
Brief introduction:
Assisted instructors in completing courses in C and C\# introductory programming courses
\begin{itemize}
  \item Responsible for laboratory maintenance, including system and local network management.
  \item Assisted with experimental course guidance.
  \item Conducted experimental report inspections.
  \item Provided work guidance and Q\&A sessions for experimental courses.
\end{itemize}

\datedsubsection{\textbf{Beijing Glory PKPM Technology Co., Ltd}, Beijing, China}{Jun. 2022 -- Jul. 2022}
\role{Python}{Software Engineer}
Brief introduction:
Using STC8H8K64U MCU and OneNet Open IoT to control the valve.
\begin{itemize}
  \item Learned to set up BIM Base and Python for a Visual Studio Code development environment.
  \item Adopted the “pyp3d” library for parametric modeling.
  \item Completed multiple model experiments, including parametric modeling of a cube, an arc, a line, a sphere, a section, a loft, a cylinder, and an abutment.
  \item Imported the `.py` file into the BIM Base Kit.
  \item Packed the model into a BFA file to encrypt model data and prevent script leakage.
\end{itemize}

\section{\texorpdfstring{\textbf{\faicon{list-check}}\ Projects}{Projects}}

\datedsubsection{\textbf{AQIoT @ CASLab CWRU}}{Oct. 2024 -- Present}
\role{Python, Shell Script}{Research Assistant}
Brief introduction: A Raspberry Pi-based air quality monitoring system
\begin{itemize}
  \item Develop a shell script to customize RasPi image with the necessary software and libraries and certain configurations.
  \item Utilize Python and Adafruit AQ sensor libraries to read air quality data on Raspberry Pi.
  \item Implement a Linux systemd service to run the Python script in the background.
  \item Add documentation and instructions and GitHub rules for the project.
\end{itemize}


\datedsubsection{\textbf{UAV Cluster Flight Control \& Design}}{Jun. 2023 -- Aug. 2023}
\role{Autodesk Maya 3D}{Research Attendant}
\begin{itemize}
  \item Learned to connect multiple drones to a terminal control client (DGCS).
  \item Ensured the drone cluster’s flight would not strike obstacles or buildings.
  \item Wrote a script for UAV Cluster Flight in Autodesk Maya 3D software using the DAMODA Cluster Flight Editor plugin.
  \item Modified several take-off and landing positions; Altered the flying route destination; Added LED controls to indicate shape, model, or image.
\end{itemize}

\datedsubsection{\textbf{Merriam-Webster Dictionary Wrapper}}{Mar. 2023 -- Sep. 2023}
\role{Python}{Individual Project}
Brief introduction: An offline dictionary
\begin{itemize}
  \item Used the Python library “requests” to generate HTML requests and display web pages.
  \item Utilized “lxml.etree” for parsing HTML content to wrap entries.
  \item Converted the thesaurus of Merriam-Webster Dictionary into a local HTML file.
  \item Saved the raw HTML file and converted it to a `.xls` file with text descriptions.
  \item Employed MDX Builder to package the `.xls` file into an `.mdx` dictionary file for use in MDict.
\end{itemize}

\datedsubsection{\textbf{Personal Blog}}{Feb. 2022 -- Present}
\role{Markdown, LaTeX, HTML, Linux}{Individual Project}
Brief introduction: Now using Hugo (Hexo before) as the framework, hosted a website on GitHub Pagesand Vercel.
\begin{itemize}
  \item Enhanced module appearance via CSS files.
  \item Employed GitHub Actions to monitor remote branch changes and update the website.
  \item Utilized DNSpod to perform domestic and international line traffic controling (Vercel for CN GEOIP and GitHub Pages for others) and domain binding.
  \item Used Twikoo as the comment module and deployed the database file containing reviewer information and comment-related content into MongoDB.
  \item Connected Twikoo to the database via its API through Vercel.
  \item Utilized the sm.ms image hosting service API to automatically upload reviewer images to the image bed.
  \item Employed Algolia as the index module to fulfill title matching and full-text search functions.
  \item Used JsDelivr to compress website static resources to increase access speed.
\end{itemize}

\datedsubsection{\textbf{Cloud Server Maintenance and Applications}}{Nov. 2022 -- Nov. 2023}
\role{Linux}{Individual Project}
Brief introduction: Configured Docker environment in Ubuntu to set up Minecraft servers suitable across versions by separating specific JRE environment versions; set up many game servers and deployed a music bot for KOOK (IM software like Discord) via open source docker image

\datedsubsection{\textbf{STC Series Microcomputer Application}}{Nov. 2020 -- Dec. 2020}
\role{C, Keil}{Individual Project}
\begin{itemize}
  \item Learned assembly language programming for STC8 series microcontrollers.
  \item Connected an LED module to a microcontroller via wiring after writing assembly code in μVision and flashing it to the microcontroller.
  \item Implemented basic IO operation experiments to control the on/off states of specific LEDs and an external switch interrupt.
  \item Conducted a digital tube experiment that provided imaging of 0 to F sixteen-digit numbers.
  \item Performed a parallel AD conversion experiment by binding the pins of the AD acquisition module and the IO port of the microcontroller in a KEIL environment.
  \item Converted the voltage analog quantity into a digital one through an assembly program.
  \item Displayed the corresponding numbers through 8 LEDs connected to the IO port of the microcontroller.
\end{itemize}

\datedsubsection{\textbf{Field-Programmable Gate Array (FPGA) Application}}{Oct. 2020 -- Noc. 2020}
\role{C, Keil}{Individual Project}
\begin{itemize}
  \item Used the EP4CE6-FPGA core board to complete digital programmable logic design experiments in Quartus II 13.0 based on the EP4CE6E22C8 experimental system hardware platform using Verilog language.
  \item Controlled four LED lights (D1-D4) by employing an FPGA solution to represent four-digit binary numbers.
  \item Switched between addition and subtraction counters using two switches and displayed the results through a digital tube.
  \item Used 74HC595 and 74LS138 for serial-to-parallel conversions to print my name on a 16\*16 monochrome dot matrix.
\end{itemize}

\datedsubsection{\textbf{C Programming Practice}}{Nov. 2018 -- Dec. 2018}
\role{C}{Individual Project}
Brief introduction: Programmed a parking lot management system to offer vehicle parking space information that could be added, deleted, or modified on demand; created software to enable a parking lot search for cars by parking space and license plate numbers

\section{\texorpdfstring{\textbf{\faicon{user-group}}\ Group Experience}{Group Experience}}
\datedsubsection{\textbf{Computing and Society Lab@CWRU}}{ Oct. 2024 -- Present}
\role{Research Assistant}{}
Brief introduction: Researching on project focusing on providing air quality sensing in urban environments.

\datedsubsection{\textbf{Student Union of CUMTB}}{Sep. 2018 -- Aug. 2020}
\role{Administrative Officer}{Department Leader}
Brief introduction: Served as an officer (for the first year) and administrator of the Science and Technology Department.
\begin{itemize}
  \item Taught members how to use Adobe Photoshop, Premiere Pro, and After Effects for poster design and video editing.
  \item Employed Resolume’s Arena for stage control during a welcoming and graduation party organized by the college.
  \item Designed dormitory door and bed stickers for first-year students.
  \item Utilized Adobe InDesign to create student handbooks.
\end{itemize}

\section{\texorpdfstring{\textbf{\faicon{gears}}\ Skills}{Skills}}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == C++ > Python > Java
  \item Platforms: Windows, Linux
  \item Other Skills: Photoshop, Premiere, After Effects, Piano, Soccer, Painting
\end{itemize}

\section{\texorpdfstring{\textbf{\faicon{award}}\ Honors and Awards}{Honors and Awards}}
\datedline{\textit{\nth{3} Prize}, Award for Campus Undergraduate Electronics Design Contest}{Jun. 2020}
\datedline{\textit{\nth{2} Prize}, Award for Campus Arduino Car Patrol Contest}{Nov. 2019}
\datedline{\textit{\nth{3} Prize}, Award for Campus ACM/ICPC}{Nov. 2018}
\datedline{\textit{\nth{1} Prize}, Award for Agricultural Bank of China Card Design Competition}{Oct. 2018}
% \datedline{Other awards}{2015}

\section{\texorpdfstring{\textbf{\faicon{circle-info}}\ Miscellaneous}{Miscellaneous}}
\begin{itemize}[parsep=0.5ex]
  \item Blog: \url{https://aphcity.top}
  \item GitHub: \url{https://github.com/Aphcity}
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% References (if needed)
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
